---
title: "Data 607 Week 02"
author: "A H M Shahparan"
date: "2/11/2018"
output: html_document
---

###Task:</br>
Choose six recent popular movies.  Ask at least five people that you know (friends, family, classmates, imaginary friends) to rate each of these movie that they have seen on a scale of 1 to 5.  Take the results (observations) and store them in a SQL database.  Load the information into an R dataframe.

Your deliverables should include your SQL scripts and your R Markdown code, posted to GitHub. This is by design a very open ended assignment.  A variety of reasonable approaches are acceptable.  You can (and should) blank out your SQL password if your solution requires it; otherwise, full credit requires that your code is “reproducible,” with the assumption that I have the same database server and R software.

###Solution:</br>
```{r}
if (!require('RMySQL')) install.packages('RMySQL')
```

```{r}
library(RMySQL)
```
####Database Access:
#####Database properties to access the database-
```{r}
myLocalUserName <- 'root'
myLocalPassword <- 'root'
myLocalDbName <- 'moviesta'
myLocalHost <- 'localhost'
```
#####Connecting the database-
```{r}
mydb = dbConnect(MySQL(), user=myLocalUserName, password=myLocalPassword, dbname=myLocalDbName, host=myLocalHost)
```
#####Getting list of database tables-
```{r}
dbListTables(mydb)
```

####Queries into the database:
#####Retreiving the 'users' table from database-
```{r}
users <- dbSendQuery(mydb, 'SELECT * FROM users')
dbFetch(users)
```
#####Retreiving the 'movies' table from database-
```{r}
movies <- dbSendQuery(mydb, 'SELECT * FROM movies')
dbFetch(movies)
```
#####Retreiving the 'ratings' table from database-
```{r}
ratings <- dbSendQuery(mydb, 'SELECT * FROM ratings')
dbFetch(ratings)
```
#####Retreiving all relational data for the 'rating' table-
```{r}
moviesta = dbSendQuery(mydb, "SELECT 
M.movieName As 'Movie',
U.userName As 'User',
R.rating As 'Rating',
R.comment AS 'Comment'
FROM movies AS M
JOIN ratings AS R
ON M.movieID = R.movie
JOIN users AS U
ON U.userID = R.user;")
dbFetch(moviesta)
```

